%%=============================================================================
%% Inleiding
%%=============================================================================

\chapter{\IfLanguageName{dutch}{Inleiding}{Introduction}}
\label{ch:inleiding}

There is no denying that everything is changing rapidly. For most people it is even so much that keeping up is really difficult.
Look at the phone industry: every year or even half a year a brand comes out with a new phone. Yet most people don't even know what the difference is with the 'older' version.
A better camera, 5G, or some other features nobody ever heard of. But do these really have a benefit? Or is it just a selling trick?
That is what this study is trying to figure out, only it won't be on phones but on quantum computers.

\section{\IfLanguageName{dutch}{Probleemstelling}{Problem Statement}}
\label{sec:probleemstelling}
Quantum computing is next big thing, or is it? Researches have been busy with quantum computing for forty-some years.
Now that the bigger companies, like IBM or Google, are also looking into it, it is heard of more and more. 
But is it really the next big thing? And if so what are the effects it will have on the industry?
This knowledge can be helpful for managers who want to start using quantum computing in their business, so they know the benefits and even the risks for the big investment they are making.
It also may help researchers in improving their quantum computers. By knowing what the bottlenecks are, they might look into them to improve it or they might go all in on the advantages and better those even more.

\section{\IfLanguageName{dutch}{Onderzoeksvraag}{Research questions}}
\label{sec:onderzoeksvraag}

The function of this study is to gain insight on what the effect of quantum computers can be on the industry.
Not only the benefits, but also the drawbacks should be investigated. In order to do so, there will be a comparison between a 'normal' algorithm and a quantum algorithm.
In the comparison the time and space complexity of both algorithms will be investigated in section \ref*{subsec:Complexities}.
To complete the study the next questions will be answered:

\begin{itemize}
  \item What is the difference between quantum computing and classic computing? The comparison should be very basic but for some specific items it will go a bit more in depth, like the time-space complexities.
  \item Does the amount of inputs on the algorithms have a significant effect on the time it takes to run the algorithm?
  \item What are the most important business processes that can be improved with quantum computing?
  \item What is the effect of quantum computing on these processes?
\end{itemize}

\section{\IfLanguageName{dutch}{Onderzoeksdoelstelling}{Research objective}}
\label{sec:onderzoeksdoelstelling}

Based on the research question the following list should definitely be in the research:

\begin{itemize}
  \item A clear explanation on what quantum computing is.
  \item A study on differences between classic and quantum computing.
  \item A classic algorithm that can be translated into a quantum algorithm.
  \item A study on the time-space complexity of both algorithms
  \item A survey to find the most important business processes.
  \item A study on the effects of quantum computing on the found processes.
\end{itemize}

\section{\IfLanguageName{dutch}{Opzet van deze bachelorproef}{Structure of this bachelor thesis}}
\label{sec:opzet-bachelorproef}

% Het is gebruikelijk aan het einde van de inleiding een overzicht te
% geven van de opbouw van de rest van de tekst. Deze sectie bevat al een aanzet
% die je kan aanvullen/aanpassen in functie van je eigen tekst.
The rest of the thesis will be as followed:

Chapter~\ref{ch:stand-van-zaken} will give an answer to what quantum computing is, what algorithms will be used and a survey will be constructed. \\
In chapter ~\ref{ch:methodologie} the methodology will be given. How will the study be conducted to be sure the answers are clear and correct. \\
And in the last chapter~\ref{ch:conclusie} the conclusion of this study will be given. What are the effect on the industry and what can we do with these.
