%%=============================================================================
%% Voorwoord
%%=============================================================================

\chapter*{\IfLanguageName{dutch}{Woord vooraf}{Preface}}
\label{ch:voorwoord}

%% TODO:
%% Het voorwoord is het enige deel van de bachelorproef waar je vanuit je
%% eigen standpunt (``ik-vorm'') mag schrijven. Je kan hier bv. motiveren
%% waarom jij het onderwerp wil bespreken.
%% Vergeet ook niet te bedanken wie je geholpen/gesteund/... heeft

I have always had a very scientific background. I've studied science-mathematics in high school, tried industrial engineering and I'm still interested in scientific topics.
So, when I saw a proposal for writing a thesis in quantum computing i did not hesitate.
And even though I did not have any knowledge of quantum computing, I find it really interesting and wanted to know if quantum computing could have benefits outside the research domain.
After doing the study I found out that businesses indeed could really gain from it. But, at this moment the technology is not developed enough to be implemented into businesses.
This also made me realize I might want to go further in this discipline and make a career in it. Because I do think that with some more advanced research this could have a big impact on the world.


This would not have been possible without the help of others.
I would like to thank Antonia Pierreux and Robbe Coudenys, they helped me with the structure and the proofreading of this paper.
Then I would like to thank Cathy Lecoutre for proofreading this thesis.
I would like to thank Florian Unseld and Pablo Cova Fariña for giving me insights and recommendations on books to read about this topic.
Lastly, I would like to thank my girlfriend, friends and parents to support me throughout my studies, it would not have been possible without them.
